>

### 2019-05-10 paper/spinifex-paper.tex
Add angle notation to view_manip_space2().
algorithm details

\begin{itemize}
\tightlist
\item
  \(\textbf{X}\), the data, an \(n \times p\) numeric matrix to be
  projected to 2D.
\item
  \(\textbf{B} = (B_1,~ B_2)\), any 2D orthonormal projection basis,
  \(p \times 2\) matrix, describing the projection from \(p\) to two
  dimensions. We will call this the ``original projection'' because it
  is the starting point for the manual tour.
\item
  \(\textbf{e}\), a 1D coordinate basis vector of length \(p\) with the
  \(k-\)th element set to one, where \(k\) is the index of the variable
  to manipulate, called the ``manip var''.
\item
  \(\theta_i\), the sequence of angles of in-projection-plane rotation,
  for example, on the reference axes.
\item
  \(\phi_i\), the sequence of angles of out-of-projection-plane
  rotation, coming into the manipulation space.
\end{itemize}

@@

\hypertarget{step-0-set-up}{%
\subsection{Step 0) Set up}\label{step-0-set-up}}

@@

\hypertarget{step-1-choose-manip-variable}{%
\subsection{Step 1) Choose manip
variable}\label{step-1-choose-manip-variable}}

@@

\hypertarget{step-2-create-the-3d-manip-space}{%
\subsection{Step 2) Create the 3D manip
space}\label{step-2-create-the-3d-manip-space}}

@@

\hypertarget{step-3-generate-rotation}{%
\subsection{Step 3) Generate rotation}\label{step-3-generate-rotation}}

@@

Let:

\begin{itemize}
  \item[$c_\theta$] be the cosine of $\theta$
  \item[$c_\phi$]   be the cosine of $\phi_i$
  \item[$s_\theta$] be the sine of   $\theta$
  \item[$s_\phi$]   be the sine of   $\phi_i$
  \item[$\textbf{U}$] be the axis of rotation for $\phi$.
\end{itemize}

@@

A note on application: \(\phi\) is the angle relative to the initial
value of \(\phi\), we find the transformation \(\phi_i\) - \(\phi_1\)
useful to think about \(\phi\) relative to the basis plane.
Additionally, the value of \(\phi\) may be out of phase by a factor of
pi. If the manip variable doesn't move as expected these are the first
places to check.

@@

\hypertarget{sec:display}{%
\section{Data in projection-space}\label{sec:display}}

>>>>

\begin{itemize}
\tightlist
\item
  \(\textbf{X}\), the data, an \(n \times p\) numeric matrix to be
  projected to 2D.
\item
  \(\textbf{B} = (B_1,~ B_2)\), any 2D orthonormal projection basis,
  \(p \times 2\) matrix, describing the projection from \(p\) to two
  dimensions. We will call this the ``original projection'' because it
  is the starting point for the manual tour.
\item
  \(\textbf{e}\), a 1D coordinate basis vector of length \(p\) with the
  \(k-\)th element set to one, where \(k\) is the index of the variable
  to manipulate, called the ``manip var''.
\item
  \(\theta\), the angle of in-projection-plane rotation, for example, on
  the reference axes; \(c_\theta, s_\theta\) are the cosine and sine.
\item
  \(\phi\), the angle of out-of-projection-plane rotation, into the
  manipulation space; \(c_\phi, s_\phi\) are the cosine and sine.
\item
  \(\textbf{U}\) is the axis of rotation for \(\phi\).
\end{itemize}

@@

\hypertarget{steps}{%
\subsection{Steps}\label{steps}}

\hypertarget{step-0-set-up}{%
\subsubsection{Step 0) Set up}\label{step-0-set-up}}

@@

\hypertarget{step-1-choose-manip-variable}{%
\subsubsection{Step 1) Choose manip
variable}\label{step-1-choose-manip-variable}}

@@

\hypertarget{step-2-create-the-3d-manip-space}{%
\subsubsection{Step 2) Create the 3D manip
space}\label{step-2-create-the-3d-manip-space}}

@@

\hypertarget{step-3-generate-rotation}{%
\subsubsection{Step 3) Generate
rotation}\label{step-3-generate-rotation}}

@@

@@

\hypertarget{creating-the-animation}{%
\subsection{Creating the animation}\label{creating-the-animation}}

The steps outlined above can be used to create any arbitrary rotation in
the manip space. To use these for sensitivity analysis, the radial
rotation is built into an animation where the manip variable is rotated
fully into the projection, completely out, and then back to the start.
This involves changing \(\phi\), the angle relative to its initial
value.

When \(\phi\) is XXX the manip var is completely in the projection, and
when \(\phi\) is not contributing at all.

\hypertarget{sequence-of-phi_i}{%
\subsubsection{\texorpdfstring{Sequence of
\(\phi_i\)}{Sequence of \textbackslash phi\_i}}\label{sequence-of-phi_i}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Set initial value to be \(\phi_1\).
\item
  Set an angle value (\(\Delta_\phi\)) that sets the step size to make
  in rotating the manip var into and out of the projection. (Note: Using
  angle value to control this is consistent with the tour algorithm, as
  implemented in the \CRANpkg{tourr}. )
\item
  Step towards \(0\), where the manip var has a completely in the
  projection.
\item
  Step towards XXX where the manip variable has no contribution.
\item
  Step back to \(\phi_1\).
\end{enumerate}

In each of steps 3-5, a small step may be made to bring it exactly to
the end position.

\hypertarget{checks-that-need-to-be-made}{%
\subsubsection{Checks that need to be
made}\label{checks-that-need-to-be-made}}

find the transformation \(\phi_i\) - \(\phi_1\) useful to think about
\(\phi\) relative to the basis plane. Additionally, the value of
\(\phi\) may be out of phase by a factor of pi. If the manip variable
doesn't move as expected these are the first places to check.

@@

\hypertarget{sec:display}{%
\subsection{Data in projection-space}\label{sec:display}}

### 2019-05-10 paper/spinifex_paper.Rmd
algorithm details

- $\textbf{X}$, the data, an $n \times p$ numeric matrix to be projected to 2D.
- $\textbf{B} = (B_1,~ B_2)$, any 2D orthonormal projection basis, $p \times 2$ matrix, describing the projection from $p$ to two dimensions. We will call this the "original projection" because it is the starting point for the manual tour.
- $\textbf{e}$, a 1D coordinate basis vector of length $p$ with the $k-$th element set to one, where $k$ is the index of the variable to manipulate, called the "manip var".
- $\theta_i$, the sequence of angles of in-projection-plane rotation, for example, on the reference axes.
- $\phi_i$, the sequence of angles of out-of-projection-plane rotation, coming into the manipulation space.

@@

## Step 0) Set up

@@

## Step 1) Choose manip variable

@@

## Step 2) Create the 3D manip space

@@

## Step 3) Generate rotation

@@

Let:
\begin{itemize}
  \item[$c_\theta$] be the cosine of $\theta$
  \item[$c_\phi$]   be the cosine of $\phi_i$
  \item[$s_\theta$] be the sine of   $\theta$
  \item[$s_\phi$]   be the sine of   $\phi_i$
  \item[$\textbf{U}$] be the axis of rotation for $\phi$.
\end{itemize}

@@

<!--  phi transform and application note -->
A note on application: $\phi$ is the angle relative to the initial value of $\phi$, we find the transformation $\phi_i$ - $\phi_1$ useful to think about $\phi$ relative to the basis plane. Additionally, the value of $\phi$ may be out of phase by a factor of pi. If the manip variable doesn't move as expected these are the first places to check.

@@

# Data in projection-space {#sec:display}

>>>>

- $\textbf{X}$, the data, an $n \times p$ numeric matrix to be projected to 2D.
- $\textbf{B} = (B_1,~ B_2)$, any 2D orthonormal projection basis, $p \times 2$ matrix, describing the projection from $p$ to two dimensions. We will call this the "original projection" because it is the starting point for the manual tour.
- $\textbf{e}$, a 1D coordinate basis vector of length $p$ with the $k-$th element set to one, where $k$ is the index of the variable to manipulate, called the "manip var".
- $\theta$, the angle of in-projection-plane rotation, for example, on the reference axes; $c_\theta, s_\theta$ are the cosine and sine.
- $\phi$, the angle of out-of-projection-plane rotation, into the manipulation space; $c_\phi, s_\phi$ are the cosine and sine.
- $\textbf{U}$ is the axis of rotation for $\phi$.

@@

## Steps
### Step 0) Set up

@@

### Step 1) Choose manip variable

@@

### Step 2) Create the 3D manip space

@@

### Step 3) Generate rotation

@@

@@

## Creating the animation

<!--  phi transform and animation -->
The steps outlined above can be used to create any arbitrary rotation in the manip space. To use these for sensitivity analysis, the radial rotation is built into an animation where the manip variable is rotated fully into the projection, completely out, and then back to the start. This involves changing $\phi$, the angle relative to its initial value.

When $\phi$ is XXX the manip var is completely in the projection, and when $\phi$ is not contributing at all.

### Sequence of $\phi_i$

1. Set initial value to be $\phi_1$.
2. Set an angle value ($\Delta_\phi$) that sets the step size to make in rotating the manip var into and out of the projection. (Note: Using angle value to control this is consistent with the tour algorithm, as implemented in the \CRANpkg{tourr}. )
3. Step towards $0$, where the manip var has a completely in the projection.
4. Step towards XXX where the manip variable has no contribution.
5. Step back to $\phi_1$.

In each of steps 3-5, a small step may be made to bring it exactly to the end position.

### Checks that need to be made

find the transformation $\phi_i$ - $\phi_1$ useful to think about $\phi$ relative to the basis plane. Additionally, the value of $\phi$ may be out of phase by a factor of pi. If the manip variable doesn't move as expected these are the first places to check.

@@

## Data in projection-space {#sec:display}
